Working with Code environments in texor

### 2023-07-22 supplement/code-env/code-example.tex
Update Code environment supplementary material

\section{Code in Table Environments}

@@

\section{Code chunks using Schunk}

\begin{Schunk}
Input :
\begin{Sinput}
print("Hello world")
\end{Sinput}
Output :
\begin{Soutput}
[1] "hello world"
\end{Soutput}

\end{Schunk}
\section{Summary}

@@

\bibitem[Fairbairns, Duggan, Schöpf, Eijkhout (2011)]{moreverb}
R.~ Fairbairns, A.~ Duggan, R.~ Schöpf and V.~ Eijkhout
\newblock The moreverb package documentation
\newblock \emph{CTAN} \penalty0 2011
\newblock URL \url{https://mirror.niser.ac.in/ctan/macros/latex/contrib/moreverb/moreverb.pdf}
\end{thebibliography}

>>>>

\section{Code in Table Environments}
We can use code environments in a table using minipage environments.

Table \ref{table:2} is an example of table with code environments within a table.

\begin{table}[htbp]
\centering
  \begin{tabular}{|c | c |}
    \hline
    Language & Function Defination Syntax \\
    \hline
    R & \begin{minipage}{0.75\textwidth}
\vspace{1mm}
\begin{example}
fun <- function(){
  print("A function in R")
  return(0)
}

\end{example}
\end{minipage}\\
\hline
Python & \begin{minipage}{0.75\textwidth}
\vspace{1mm}
\begin{example}
def fun():
  print("A function in Python")

\end{example}
\end{minipage}\\
\hline

Lua & \begin{minipage}{0.75\textwidth}
\vspace{1mm}
\begin{example}
function fun()
  print("A function in Lua")
end

\end{example}
\end{minipage}\\
\hline

C & \begin{minipage}{0.75\textwidth}
\vspace{1mm}
\begin{example}
int fun() {
  printf("A function in C");
  return 0;
}

\end{example}
\end{minipage}\\
\hline
\end{tabular}
\caption{Code in a table}
\label{table:2}
\end{table}

A similar arrangement can be had for figures/plots besides code environment.
Table \ref{table:3} demonstrates a table with code and figure.
\begin{table}[htbp]
  \centering
  \begin{tabular}{| c | c |}
  \hline
  Code & Plot\\
    \hline
    \begin{minipage}{0.45\textwidth}
\vspace{1mm}
\begin{example}
x <- 1:100
y <- dbinom(x,100,prob = 0.5)
plot(x,y)
\end{example}
    \end{minipage} &
    \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{binom}
    \end{minipage}\\
    \hline
  \end{tabular}
  \caption{Code and Plot side by side}
  \label{table:3}
\end{table}

@@

Using inline code in LaTeX is possible using \verb|\verb| command.
It would be repoduced similarly, as a Inline code element.
\begin{verbatim}
\verb|x <- 1:100|
\end{verbatim}
will be represented as \verb|x <- 1:100| in Inline format.

\section{Code chunks using Schunk}
Code chunks within an \verb|Schunk| environment to demonstrate Input/Output

\begin{Schunk}
Input :
\begin{Sinput}
print("Hello world")
\end{Sinput}
Output :
\begin{Soutput}
[1] "hello world"
\end{Soutput}
\end{Schunk}

Similar arrangement can be had for Plots as well using figure environnment.

\begin{Schunk}
Input :
\begin{Sinput}
x <- 1:100
y <- dbinom(x,100,prob = 0.5)
plot(x,y)
\end{Sinput}
Output :\\
\includegraphics[width=0.5\textwidth]{binom}
\end{Schunk}

\section{Summary}

@@

\bibitem[Fairbairns, Duggan, Schöpf, Eijkhout (2011)]{moreverb}
R.~ Fairbairns, A.~ Duggan, R.~ Schöpf and V.~ Eijkhout
\newblock The moreverb package documentation
\newblock \emph{CTAN} \penalty0 2011
\newblock URL \url{https://mirror.niser.ac.in/ctan/macros/latex/contrib/moreverb/moreverb.pdf}

\end{thebibliography}
